\begin{thebibliography}{99} % the second arg is for the width of the item label
\bibitem{thePiano}
  Robert Palmieri
  \emph{The Piano: An Encclopedia}
  2e,
  Routledge,  
  p. 299-303
\bibitem{wiki}
  \url{http://en.wikipedia.org/wiki/Gongche_notation}
\bibitem{wikiSoundLocalization}
  \url{http://en.wikipedia.org/wiki/Sound_localization}
\bibitem{wikiFantasia}
  \url{http://en.wikipedia.org/wiki/Fantasia_(film)}
\bibitem{mixingAudio}
  Roey Izhaki
  \emph{Mixing Audio: Concepts, Practices and Tools}
  Focal Press,
  p. 185
\bibitem{midiSpec}
  \url{http://www.midi.org/techspecs/rp36.php}
\bibitem{britannica}
  \emph{Encyclopædia Britannica}, vol. 24, p. 536
\bibitem{designPatterns}
  Gamma, R Helm, R Johnson, J Vlissides, 
  \emph{Design Patterns: Elements of Reusable Object-Oriented Software},
  Addison-Wesley, p. 163, 293, 
  1994
\bibitem{chinaMusicHistory}
  薛宗明《中國音樂史．樂譜篇》, p. 549
\bibitem{chinaEncyclopedia}
  《中國大百科全書．音樂舞蹈》, p. 299
\bibitem{iring}
   清蔚科技，「哼唱鈴i-Ring」，\url{http://www.cweb.com.tw/About/AboutIndex.hi}，2009。
\bibitem{musicMasterWorks}
   Aspire Software, “Music MasterWorks,” \url{http://www.musicmasterworks.com/}, 2009.
\bibitem{sibelius}
   Avid Technology, “Sibelius 5,” \url{http://www.sibelius.com/}, 2009.
\bibitem{denemo}
   Denemo 0.82, \url{http://www.denemo.org/}, 2009.
\bibitem{endPointDetection}
End Point Detection, \url{http://neural.cs.nthu.edu.tw/jang/books/audioSignalProcessing/epdIntro.asp?title=6-1%20Introduction%20to%20End-Point%20Detection%20}
\bibitem{theABGuide}
   Eric Taylor, “The AB Guide to Music Theory Part I,” The Associated Board of the Royal Schools of Music, p. 17, 1989. 
\bibitem{soundPressure}
   Sound Pressure, \url{http://en.wikipedia.org/wiki/Sound_pressure}, 2009
\bibitem{virtualSurroundSound}
   Tracy V. Wilson, “How Virtual Surround Sound Works” \url{http://electronics.howstuffworks.com/virtual-surround-sound.htm/printable}, 2009
\bibitem{lilypond}
   LilyPond, \url{http://lilypond.org/}, 2009.
\bibitem{finale2009}
   MakeMusic, “Finale 2009,” \url{http://www.finalemusic.com/}, 2009.
\bibitem{midiTuningStrandard}
   MIDI Tuning Standard (MTS) %>>>>>>>>>>>>>>>>>>
\bibitem{praat}
   Paul Boersma & David WeeninkPraat, “Praat,” \url{http://www.praat.org/}, 2009.
\bibitem{pianoRoll}
   Piano Roll, \url{http://en.wikipedia.org/wiki/Piano_roll}
\bibitem{javaSound}
   Sun Microsystems, “Java Sound API,” \url{http://java.sun.com/products/java-media/sound/}, 2009.
\bibitem{javaPlatform}
   Sun Microsystems, “Java Platform, Standard Edition,” \url{http://java.sun.com/javase/index.jsp}, 2009
\bibitem{javaScriptinAPI}
   Sun Microsystems, “Java Scripting API,” \url{https://scripting.dev.java.net/}, 2009.
\bibitem{vocalRange}
   “Vocal Range,” \url{http://en.wikipedia.org/wiki/Vocal_range}, 2009.
\end{thebibliography}

% 參考文獻   /* 沒有書才用網頁 */

